Stochastic Variance Reduced Policy Gradient

### 2018-02-02 svrpg.tex
correzioni

\section{Hyperparameters}\label{sec:stopping}
In Reinforcement learning we have to take into account the gradient's variance.
\todomat{$\uparrow$ the opening of the section could connect better with previous sections. Declare which meta-parameters will be addressed in the section}
A common way to reduce the effect of variance is to use Adaptive Moment Estimation (Adam) \cite{kingma2014adam}, a method that computes adaptive learning rates for each parameter. Adam helps to stabilize the gradient estimate by computing adaptive learning rates for each parameter based on the history of the gradients' variance.
We use two different adam hyperparameters: one for updates tied to snapshot points and the other tied to the updates of sub-iterations points.
\todomat{$\uparrow$ explain better: it's not only two separate meta-parameters, but two separate learning rate schedules. Use notation from previous sections, \eg snaphot is usually associated with $\tilde{\vtheta}$} 
This is because we are dealing with two different variance magnitudes.
\todomat{$\uparrow$ the reason is this, but try to spend more words on it}
Denote by $\alpha_{snap}$ the last learning rate computed into the snapshot point and denote by  $\alpha_{sub-iter}$ the last learning rate computed into the sub-iteration point.

>>>>

\section{Hyperparameters}\label{sec:stopping}
In Reinforcement learning we have to take into account the gradient's variance.
\todomat{$\uparrow$ the opening of the section could connect better with previous sections. Declare which meta-parameters will be addressed in the section}
A common way to reduce the effect of variance is to use Adaptive Moment Estimation (Adam) \cite{kingma2014adam}, a method that computes adaptive learning rates for each parameter. Adam helps to stabilize the gradient estimate by computing adaptive learning rates for each parameter based on the history of the gradients' variance.
We use two different adam hyperparameters: one for updates tied to snapshot points and the other tied to the updates of sub-iterations points.
\todomat{$\uparrow$ explain better: it's not only two separate meta-parameters, but two separate learning rate schedules. Use notation from previous sections, \eg snaphot is usually associated with $\tilde{\vtheta}$} 
This is because we are dealing with two different variance magnitudes.
\todomat{$\uparrow$ the reason is this, but try to spend more words on it}
Denote by $\alpha_{snap}$ the learning rate associated to the last snapshot and denote by  $\alpha_{sub-iter}$ the learning rate associated to the current sub-iteration.
